CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-12-10 paper/ms.tex
Compare the results
Compare the two formulas for radial velocity shifts.

I plot the histogram of radial velocity shifts derived by using $v_{shift} = (c-a)*v_{pixel}$ in diagnostic figure 2 and velocity shifts against mean fiber number in diagnostic figure 3.

@@

\centerline{Diagnostic Fig.2 Histogram of radial velocity shifts}
\centerline{The formula to derive velocity shifts is $v_{shift} = (c-a)*v_{pixel}$}
\bigskip

@@

\centerline{Diagnostic Fig.3 Radial velocity shifts against mean fiber number}
\centerline{The formula to derive velocity shifts is $v_{shift} = (c-a)*v_{pixel}$}
\bigskip

We also plot the four stars with biggest radial velocity shifts, which are in figure 13. The formula I use is $v_{shift} = (c-a)*v_{pixel}$.

@@

\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest radial velocity shifts.}

@@

The original histogram of radial velocity shifts for figure 11.

@@

\centerline{Diagnostic Fig.5 Histogram of radial velocity shifts}
\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
\bigskip

@@

\centerline{Diagnostic Fig.6 Radial velocity shifts against mean fiber number}
\centerline{The formula to derive velocity shifts is $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$}
\bigskip

To check which method is better, we choose the four stars with smallest abs(a-c). These four stars have abs(a-c) smaller than 0.001 and we think their radial velocity shifts are 0. We call $v_{shift} = {{(c-a)*v_{pixel}}\over{4\cdot(a+c-2b)}}$ method A and $v_{shift} = (c-a)*v_{pixel}$ method B.

First, move the data spectrum of the four stars one pixel left and the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$

@@

\centerline{Diagnostic Fig.7 Move the data spectrum one pixel left.}
\centerline{the radial velocity shift should be $-v_{pixel}$= -4144.68$m/s$}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

Then, move the data spectrum of the four stars one pixel right and the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$

@@

\centerline{Diagnostic Fig.8 Move the data spectrum one pixel right.}
\centerline{the radial velocity shift should be $v_{pixel}$= 4144.68$m/s$}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

>>>>

@@

\centerline{Diagnostic Fig.2 Four fake stars with Gaussian wave pack spectrums}
\centerline{The green line is the template and the black line is the observation}
\bigskip

@@

\centerline{Diagnostic Fig.3 Spectrum of the four stars with biggest c-a}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
\bigskip

@@

\centerline{Diagnostic Fig.4 Spectrum of the four stars with biggest a-c}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}

@@

@@

\centerline{Diagnostic Fig.5 Spectrum of the four stars with biggest a+c-2b}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
\bigskip

@@

\centerline{Diagnostic Fig.6 Spectrum of the four stars with b closest to 1}
\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum}
\bigskip

@@

$v_cc$ is the velocity shift from the cross-correlation. $v_David$ is the velocity shift from David's formula. $v_Jason$ is the velocity shift from Jason's formula.

\centerline{Diagnostic Fig.7 $v_cc$ vs$v_David$}

@@

@@

\centerline{Diagnostic Fig.8 $v_cc$ vs$v_Jason$}

\begin{center}
\includegraphics[width=170mm]{d_figure_9.png}
\end{center}

\centerline{Diagnostic Fig.9 $v_cc$ vs$v_David$}

\begin{center}
\includegraphics[width=170mm]{d_figure_10.png}
\end{center}

\centerline{Diagnostic Fig.10 $v_cc$ vs$v_Jason$}
